An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Proofed protocol section.

\section*{Protocol}
%
The experimental protocol consisted of static measurements and walking on the
treadmill for 10 minutes under unperturbed and perturbed conditions. Before a
set of trials on the same day the following happened:
%
\begin{itemize}
  \item Calibration of the motion capture system.
  \item Subject changes into athletic shoes, shorts, sports bra, baseball
    cap, and rock climbing harness.
  \item All 47 markers are applied directly to the skin except for the heel,
    toe, and head markers.~\footnote{The sacrum and rear pelvic markers were
    placed on the shorts for a small number of the subjects}.
  \item Subjects self-reported age, gender, and mass.
  \item Height is measured by the experimentalist.
  \item Four reference photographs (front, back, right, left) are taken of
    subjects marker locations.
\end{itemize}

After obtaining informed consent and a briefing by the experimentalist on the trial protocol, the subject
follows the verbal instructions of the experimentalist and the on-screen
instructions from the video display in front of the subject. The protocol goes
as follows:
%
\begin{enumerate}
  \item Subject steps onto the treadmill and markers are identified with
    Cortex.
  \item The safety cable is attached loosely to the rock climbing harness such
    that no undue forces are acting on the subject during walking, but that the
    harness will prevent a full fall.
  \item The subject starts by stepping on sides of treadmill so that feet don't
    touch the force plates and the force plate signals are zeroed.
  \item Once notified by the screen, the subject stands in the initialization
    pose: standing straight up, looking forward, arms out by their sides (~45
    degrees) and the event is manually recorded by the operator.
  \item A countdown to the first normal walking phase is displayed. At the end
    of the countdown the treadmill starts at the specified speed and the
    subject is instructed to walk normally, to focus on the road in the
    screen, and not to look at their feet.
  \item After 1 minute of normal walking, the longitudinal perturbation phase
    begins.
  \item After 8 minutes of walking under the influence of the perturbations,
    the normal walking phase begins.
  \item After 1 minute, a countdown is shown and the treadmill decelerates to a
    stop.
  \item The subject is instructed to step off of the force plates for 10
    seconds.
  \item The subject could take a break before each additional trial.
\end{enumerate}

>>>>

\section*{Protocol}
%
The experimental protocol consisted of both static measurements and walking on
the treadmill for 10 minutes under unperturbed and perturbed conditions. Before
a set of trials on the same day the following happened:
%
\begin{itemize}
  \item Calibration of the motion capture system using the manufacturer's
    recommended procedure.
  \item Subject changes into athletic shoes, shorts, sports bra, baseball
    cap, and rock climbing harness.
  \item All 47 markers are applied directly to the skin except for the heel,
    toe, and head markers, which were placed on the respective article of
    clothing.~\footnote{The sacrum and rear pelvic markers may have been placed
    on the shorts for a small number of the subjects}.
  \item Subjects self-reported age, gender, and mass.
  \item Height was measured by the experimentalist.
  \item Four reference photographs (front, back, right, left) were taken of
    subject's marker locations.
\end{itemize}

After obtaining informed consent and a briefing by the experimentalist on the
trial protocol, the subject followed the verbal instructions of the
experimentalist and the on-screen instructions from the video display. The
protocol for a single trial was as follows:
%
\begin{enumerate}
  \item Subject stepped onto the treadmill and markers were identified with
    Cortex.
  \item The safety rope was attached loosely to the rock climbing harness such
    that no undue forces were acting on the subject during walking, but that
    the harness would prevent a full fall.
  \item The subject started by stepping on sides of treadmill so that feet did
    not touch the force plates and the force plate signals are zeroed. This
    corresponds to the ``Force Plate Zeroing'' event.
  \item Once notified by the video display, the subject stood in the
    initialization pose: standing straight up, looking forward, arms out by
    their sides (~45 degrees) and the event, ``Calibration Pose'', was manually
    recorded by the operator.
  \item A countdown to the first normal walking phase was displayed. At the end
    of the countdown the event ``First Normal Walking'' was recorded and the
    treadmill ramped up to the specified speed and the subject was instructed
    to walk normally, to focus on the ``endless'' road on the display, and not
    to look at their feet.
  \item After 1 minute of normal walking, the longitudinal perturbation phase
    begun and was recorded as ``Longitudinal Perturbation''.
  \item After 8 minutes of walking under the influence of the perturbations,
    the second normal walking phase begun and was recorded as ``Second Normal
    Walking''.
  \item After 1 minute of normal walking, a countdown was shown on the display
    and the treadmill decelerated to a stop.
  \item The subject was instructed to step off of the force plates for 10
    seconds and the ``Unloaded End'' event was recorded.
  \item The subject could then take a rest break before each additional trial.
\end{enumerate}

Trials 6-8 included a calibration pose at the start of the trial but the event
was not explicitly recorded. In those trials, the ``TreadmillPerturbation''
event marks the beginning of longitudinal perturbations and the ``Both'' event
marks the beginning of combined longitudinal and lateral perturbations. The
force plate zeroing at the end was also not explicitly recorded.
